Computational tools for representation theory of affine Lie algebras

### 2009-07-10 AffineLieAlgebras/ACMS2009/notes.tex
Conformal embeddings started

For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
\begin{equation}
  \label{eq:105}
  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
\end{equation}
The partition function is rewritten as
\begin{equation}
  \label{eq:106}
  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
\end{equation}
$M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$. It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
\begin{equation}
  \label{eq:108}
  \begin{aligned}
    T^{\dagger}MT=S^{\dagger}MS=M,\\
    [M,S]=[M,T]=0,
  \end{aligned}
\end{equation}
and $M_{00}=1$ for the uniqueness of vacuum.

>>>>

For WZW-models the representations are determined by highest weights $\hat \lambda, \hat \xi$. Then we can write
\begin{equation}
  \label{eq:105}
  \mathcal{H}=\bigoplus_{\hat \lambda,\hat \xi\in P^{(k)}_{+}}M_{\hat \lambda,\hat \xi} L_{\hat \lambda}\otimes L_{\hat \xi}
\end{equation}
The partition function is rewritten as
\begin{equation}
  \label{eq:106}
  Z(\tau)=\sum_{\hat \lambda,\hat \xi\in P^{(k)}_{+}} \chi_{\hat \lambda}(\tau)M_{\hat \lambda\hat\xi}\bar \chi_{\hat \xi}(\bar \tau)
\end{equation}
The element of the mass matrix $M_{\hat \lambda\hat\xi}$ can be thought of as the multiplicity of primary field with weights $\hat\lambda,\hat \xi$. It has following properties:$M_{\hat \lambda\hat\xi}\in \mathbb{Z}_+$, it is modular invariant
\begin{equation}
  \label{eq:108}
  \begin{aligned}
    T^{\dagger}MT=S^{\dagger}MS=M,\\
    [M,S]=[M,T]=0,
  \end{aligned}
\end{equation}
and $M_{00}=1$ for the uniqueness of vacuum.

The simplest case of diagonal matrix $M$ corresponds to equal holomorphic and antiholomorphic conformal dimensions. There are several ways to construct non-diagonal modular invariants from diagonal \cite{difrancesco1997cft}:
\begin{itemize}
\item Method of outer automorphisms
\item Conformal embedding into bigger theory
\item Galois-transpositions
\end{itemize}
Here we will discuss conformal embeddings.

\subsubsection{Conformal embeddings}
\label{sec:conformal-embeddings}
